\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-10-21 main.tex
Updates from Overleaf

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\textwidth]{examples/images/mesh.pdf}
    \caption{Computational meshes for circular (a, b) and square (c, d) rings, without (a, c) and with (b, d) \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}. The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue. Note that optimizing the mesh does not change the total number of vertices or triangles, but tends to make the triangle density more uniform across the mesh. In this case, all four meshes (a-d) contain around 6,000 points and 12,000 triangles.}
    \label{fig:mesh}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\textwidth]{examples/images/mesh.pdf}
    \caption{Computational meshes for circular (a, b) and square (c, d) rings, without (a, c) and with (b, d) \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}. The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue. Note that optimizing the mesh does not change the total number of vertices or triangles, but tends to make the triangle size and density more uniform across the mesh. In this case, all four meshes (a-d) contain around 6,000 points and 12,000 triangles.}
    \label{fig:mesh}
\end{figure}
